Proving linearizability using forward simulations\thanks{An extended version of this paper including the missing proofs can be found at \cite{extended}.}

### 2017-05-05 draftCAV/stack.tex
TSS figure.

\vspace{-3.5mm}
\subsection{Pop Methods With Fixed Commit Points}
\vspace{-1mm}
\begin{wrapfigure}{l}{5.2cm}
\vspace{-10.5mm}
\begin{lstlisting}
struct Node{
  int data;
  int ts;
  Node* next;
  boolean taken;
};
Node* pools[maxThreads];
int TS = 0;

void push(int x) {
  Node* n = new Node(x,MAX_INT,
                        null,false);
  n->next = pools[myTID];
  pools[myTID] = n;
  int i = TS++;
  n->ts = i;
}
int pop() {
 boolean success = false;
 int maxTS = -1;
 Node* youngest = null;
 while ( !success ) {
   maxTS = -1; youngest = null;
   for(int i=0; i<maxThreads; i++){
     Node* n = pools[i];
     while (n->taken && n->next != n)
       n = n->next;
     if(maxTS < n->ts) {
       maxTS = n->ts; youngest = n;
     }
   }
   if (youngest != null)
     success=CAS(youngest->taken,
                       false,true);
 }
 return youngest->data;
}
\end{lstlisting}
\vspace{-6mm}
\caption{Time-Stamped Stack.} %We assume that every statement is atomic.}
\label{fig:TimeStamped}
\vspace{-7mm}
\end{wrapfigure}
We explain the meaning of the commit points on a simplified version of the Time-Stamped Stack~\cite{DBLP:conf/popl/DoddsHK15} ($\mathit{TSS}$, for short) given in Fig.~\ref{fig:TimeStamped}. This  implementation maintains an array of singly-linked lists, one for each thread, where list nodes contain a data value (field {\tt data}), a timestamp (field {\tt ts}), the next pointer (field {\tt next}), and a boolean flag indicating whether the node represents a value removed from the stack (field {\tt taken}). Initially, each list contains a sentinel dummy node pointing to itself with timestamp $-1$ and the flag {\tt taken} set to {\tt false}.

>>>>

\vspace{-3.5mm}
\subsection{Pop Methods With Fixed Commit Points}
\vspace{-1mm}

We explain the meaning of the commit points on a simplified version of the Time-Stamped Stack~\cite{DBLP:conf/popl/DoddsHK15} ($\mathit{TSS}$, for short) given in Fig.~\ref{fig:TimeStamped}. This  implementation maintains an array of singly-linked lists, one for each thread, where list nodes contain a data value (field {\tt data}), a timestamp (field {\tt ts}), the next pointer (field {\tt next}), and a boolean flag indicating whether the node represents a value removed from the stack (field {\tt taken}). Initially, each list contains a sentinel dummy node pointing to itself with timestamp $-1$ and the flag {\tt taken} set to {\tt false}.

\begin{figure}[t]
  \begin{minipage}[t]{0.49\linewidth}
    \begin{lstlisting}
struct Node{
  int data;
  int ts;
  Node* next;
  bool taken;
};

bool CAS(bool data, bool a, bool b);

Node* pools[maxThreads];
int TS = 0;

void push(int x) {
  Node* n =
    new Node(x,MAX_INT, null,false);
  n->next = pools[myTID];
  pools[myTID] = n;
  int i = TS++;
  n->ts = i;
}
    \end{lstlisting}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{0.49\linewidth}
    \begin{lstlisting}
int pop() {
  bool success = false;
  int maxTS = -1;
  Node* youngest = null;
  while ( !success ) {
    maxTS = -1; youngest = null;
    for(int i=0; i<maxThreads; i++) {
      Node* n = pools[i];
      while (n->taken && n->next != n)
        n = n->next;
      if(maxTS < n->ts) {
        maxTS = n->ts; youngest = n;
      }
    }
    if (youngest != null)
      success =
        CAS(youngest->taken, false, true);
  }
  return youngest->data;
}
    \end{lstlisting}
  \end{minipage}

  \caption{The Time-Stamped Stack~\cite{DBLP:conf/popl/DoddsHK15}.}
  \label{fig:TimeStamped}
\end{figure}
